### 2015-03-02 fundamentals/intro.tex
spellcheck

The cardinal purpose of a dyamic nuclear fuel cycle simulator is to calculate
the time- and facility-dependent mass flow through all or part the fuel cycle.
Dynamic nuclear fuel cycle analysis more realistically supports a range of
simulation goals than static analysis \cite{piet_dynamic_2011}. Historically,
dynamic nuclear fuel cycle simulators have calculated fuel cycle mass balances
and performance metrics derived from them using software ranging from ad hoc
spreadsheet-driven flow calculators to highly specialized system dynamics
modeling platforms. To date, current tools are often rigid rather than flexible,
fleet-based rather than discrete, or privately distributed rather than open
source. Each of these choices presents a challenge to modeling fidelity,
generality, efficiency, robustness, and scientific transparency.

@@

However, methods for calculating those metrics vary among simulators. Some
model the system of facilities, economics, and materials in static equilibrium,
while other simulators capture the dynamics of the system.  Similarly, while
some simulators discretely model batches of material and individual facilities,
others aggregate facilities into fleets and materials into streams. Simulators
can model a single aspect of the fuel cycle in great detail while neglecting
others. For example, a simulator created for policy modeling might have
excellent capability in economics while capabailities for tracking transformations in
material isotopics and the effects of isotopics on technology performance are
neglected.  The \gls{CAFCA}\cite{guerin_impact_2009} simulator is problem-oriented
in this way, having elected to neglect isotopic resolution in favor of
integral effects.

@@

The \Cyclus paradigm enables targeted contribution and collaboration within the
nuclear fuel cycle analysis community to achieve two important goals: lower the
barrier for innvoative nuclear technologies to be included in fuel cycle analysis
while improving the ability to compare simulations with and without those innovative
concepts.  This essential capability is absent in
previous simulators where user customization and extensibility were not design
objectives.  While the \emph{modular and open architecture} of
\Cyclus is necessary to meet these goals, it is not sufficient.
\emph{Agent interchangeability} is required to facilitates direct comparison
of alternative modeling methodologies and facility concepts.  Finally, \Cyclus is
applicable to a broader range of fidelities, scales, and applications than
other simulators, due to the flexibility and generality of its
\emph{\gls{ABM}} paradigm and \emph{discrete, object-oriented approach}.

>>>>

The cardinal purpose of a dynamic nuclear fuel cycle simulator is to calculate
the time- and facility-dependent mass flow through all or part the fuel cycle.
Dynamic nuclear fuel cycle analysis more realistically supports a range of
simulation goals than static analysis \cite{piet_dynamic_2011}. Historically,
dynamic nuclear fuel cycle simulators have calculated fuel cycle mass balances
and performance metrics derived from them using software ranging from ad hoc
spreadsheet-driven flow calculators to highly specialized system dynamics
modeling platforms. To date, current tools are often rigid rather than flexible,
fleet-based rather than discrete, or privately distributed rather than open
source. Each of these choices presents a challenge to modeling fidelity,
generality, efficiency, robustness, and scientific transparency.

@@

However, methods for calculating those metrics vary among simulators. Some
model the system of facilities, economics, and materials in static equilibrium,
while other simulators capture the dynamics of the system.  Similarly, while
some simulators discretely model batches of material and individual facilities,
others aggregate facilities into fleets and materials into streams. Simulators
can model a single aspect of the fuel cycle in great detail while neglecting
others. For example, a simulator created for policy modeling might have
excellent capability in economics while capabilities for tracking transformations in
material isotopics and the effects of isotopics on technology performance are
neglected.  The \gls{CAFCA}\cite{guerin_impact_2009} simulator is problem-oriented
in this way, having elected to neglect isotopic resolution in favor of
integral effects.

@@

The \Cyclus paradigm enables targeted contribution and collaboration within the
nuclear fuel cycle analysis community to achieve two important goals: lower the
barrier for innovative nuclear technologies to be included in fuel cycle analysis
while improving the ability to compare simulations with and without those innovative
concepts.  This essential capability is absent in
previous simulators where user customization and extensibility were not design
objectives.  While the \emph{modular and open architecture} of
\Cyclus is necessary to meet these goals, it is not sufficient.
\emph{Agent interchangeability} is required to facilitates direct comparison
of alternative modeling methodologies and facility concepts.  Finally, \Cyclus is
applicable to a broader range of fidelities, scales, and applications than
other simulators, due to the flexibility and generality of its
\emph{\gls{ABM}} paradigm and \emph{discrete, object-oriented approach}.
